Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
Adding a comment to a comment

\begin{definition}[Consistent: property]\label{def:consistent-prop}
	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
	\begin{equation}
    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
  \end{equation}
  % where $D_x = \Pr[Y|X=x]$.
  We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
  Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me}}
  % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
  % In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
\end{definition}

@@

\begin{restatable}[]{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
	Let a convex $\P \subseteq \simplex$ be given.
\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
% Take $\propdis: \R \times \simplex \to \reals_+$ with 
$\mu(r,p) := R_\ell(r,p)$.
Then there is a $\D$ such that
$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
\btw{Note: don't actually need $\gamma$ nonempty here.}
\end{restatable}

>>>>

\begin{definition}[Consistent: property]\label{def:consistent-prop}
	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
	\begin{equation}
    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
  \end{equation}
  % where $D_x = \Pr[Y|X=x]$.
  We simply say $(L,\psi)$ is \emph{$\propdis$-consistent} if it is $(\propdis,\D)$-consistent for some $\D$ satisfying the following: for all $p \in \P$, there exists $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$.
  Additionally, we say $(L,\psi)$ is \emph{consistent} if there is a $\propdis$ such that $(L,\psi)$ is $\propdis$-consistent.
  \raft{Ditto; hopefully this is equivalent to what was here before (commented out below)\jessie{Looks good to me \#burn}}
  % Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
  % In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
\end{definition}

@@

\begin{restatable}[]{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
	Let a convex $\P \subseteq \simplex$ be given.
%\jessiet{Defer to appendix?  Thoughts?}\raft{Let's keep it but move the proof.}
Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
% Take $\propdis: \R \times \simplex \to \reals_+$ with 
$\mu(r,p) := R_\ell(r,p)$.
Then there is a $\D$ such that
$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
\btw{Note: don't actually need $\gamma$ nonempty here.}
\end{restatable}
